---
title: "Proyecto Netflix Movies MADM"
author: "Laura Moreno, Josep Roman, Paul Ramírez"
date: "11/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Data Wrangle

## Importación de datos

#### Info de los archivos "combined_data_.txt"
The first line of each file contains the movie id followed by a colon. Each subsequent line in the file corresponds to a rating from a customer and its date in the following format:

  CustomerID,Rating,Date  
  
  * MovieIDs range from 1 to 17770 sequentially.
  * CustomerIDs range from 1 to 2649429, with gaps. There are 480189 users.
  * Ratings are on a five star (integral) scale from 1 to 5.
  * Dates have the format YYYY-MM-DD.  
  
```{r, include=FALSE}
library(tidyverse)
```


```{r}

aux=read_tsv("Raw data/combined_data_1.txt", col_names = FALSE, n_max = 30000) #lectura de las primeras 10^4 filas

```

## Orden de los datos

```{r}
aux=aux%>% mutate(fila=row_number()) #añadir columna con número de fila
filas=grep(":",aux$X1) #buscar filas con ":", filas comienzo nueva pelicula
filas_ID= aux %>% filter( fila %in% filas ) 
IDs=unique(filas_ID$X1)
reps=diff(c(filas_ID$fila,max(aux$fila)+1))
length(reps)
dim(aux)
sum(reps)
scores = aux %>% mutate(ID1=rep(filas_ID$X1,times=reps)) %>% filter(!(fila %in% filas) )

#ahora borramos los datos de la última película por si se han cortado a medias
scores = scores %>% filter( scores$fila < filas_ID$fila[length(filas_ID$fila)-1] )

# Ahora arregloamos la variable X1, y separamos la fecha en año, mes y día
scores = scores %>% separate(X1,into = c("CustomerID","Score","Date"), sep = ",")
scores = scores %>% mutate(Date_copy = Date)  %>% separate(Date_copy, into = c("Year", "Month", "Day"), sep = "-")

#Renombramos y reordenamos las variables
scores <- rename(scores, MovieID = ID1, RowID = fila)
scores = scores %>% relocate(RowID, MovieID, CustomerID, Date, Year, Month, Day, Score)

#Quitamos los ":" de el campo MovieID
scores$MovieID <- scores$MovieID %>% str_replace(":", "")

# Cambiamos los tipos de variable necesarios

scores <- scores %>% mutate(across(c(RowID:CustomerID, Year:Score), as.integer))


summary(scores)
```

Info data
```{r}
length(unique(scores$CustomerID)) #9619 usuarios distintos
table(scores$Score) # frecuencia puntuaciones
table(scores$ID) # frecuencia pelis
scores<-mutate(scores, fila=NULL) # eliminamos la columna fila
```

### Cargar csv títulos
```{r}
titles = read_csv('Raw data/movie_titles.csv', col_names=F )
head(titles)
tt<-tibble(titles)
tt <- rename(tt, ID = X1, Year = X2, Title = X3)
head(tt)
#inner_join()
```





